Himalayan Expeditions Success Analysis

### 2024-04-18 paper/paper.qmd
Simulation added and comments to all scripts added

expeditions_model <- readRDS(here("models/single_bay.rds"))
analysis_data <- read_parquet("data/analysis_data/expeditions.parquet")
predictions <- read.csv(here("data/predictions/predictions.csv"))
```

>>>>

expeditions_model <- readRDS(here("models/single_bay.rds"))
analysis_data <- read_parquet(here("data/analysis_data/expeditions.parquet"))
predictions <- read.csv(here("data/predictions/predictions.csv"))
```
